Missing years 2019 and 2020^[Code and data are available at: https://github.com/SANGWOONG-LEE/2016electionanalysis]

### 2022-04-24 outputs/paper/paper.Rmd
grammer edited overall

In order to discern the changes by the pandemic and others, I was required to research U.S society backgrounds from 2018 to 2021, and they were used along with data analysis. By plotting graphs for comparison between 2018 and 2021, I was able to sort the variables o=into three categories: Positive, Negative and unchanged reaction. For instance, for the positive reaction, there was drop in "Too much" and increase in "Too little" and vice versa for negative category. National spending on welfare and drug belong to the positive group. On the other hand, national spending on arms, or foreign aids belong to negative. Of course, there exists exceptions within the groups, and they are going to be dealt with in result and discussion session.

@@

Since I do not have exact y-value in my data, I am going to create representative from the three categories: positive, negative and unchanged, then double check whether they belong to appropriate groups or not. To do that, I am going to use multiple linear regression model. Since changes must move together once they belong to same groups, I decided that multiple linear regression model could explain better than others. In order to sort variables into the three groups, I followed the result from data session, and set changes less than 5% as unchanged. The outcome is as followed:

@@

## what is something that we learn about the world?
We have learned that there existed changes in U.S citizens' mind after COVID-19 breakout. However, considering the shock that COVID-19 gave us unlike other viruses such as Ebola, the change was subtle. In other words, the world keeps going by coping with such challenges.

@@

## End Page

Thank you for participating in our survey. If you have any questions please do not hesitate to contact us.
sangwoong.lee@maill.utoronto.ca

>>>>

In order to discern the changes by the pandemic and others, I was required to research U.S society backgrounds from 2018 to 2021, and they were used along with data analysis. By plotting graphs for comparison between 2018 and 2021, I was able to sort the variables into three categories: Positive, Negative and unchanged reaction. For instance, for the positive reaction, there was drop in "Too much" and increase in "Too little" or "About right", and vice versa for negative category. National spending on welfare and drug belong to the positive group. On the other hand, national spending on arms, or foreign aids belong to negative. Of course, there exists exceptions within the groups, and they are going to be dealt with in result and discussion session.

@@

Since I do not have exact y-value in my data, I am going to create representative from the three categories: positive, negative and unchanged, then double check whether they belong to appropriate groups or not. To do that, I am going to use multiple linear regression model. Since direction of changes must move together once they belong to same groups, I decided that multiple linear regression model could explain better than others. In order to sort variables into the three groups, I followed the result from data session, and set changes less than 5% as unchanged. The outcome is as followed:

@@

## what is something that we learn about the world?
We have learned that there existed changes in U.S citizens' mind after COVID-19 breakout. However, considering the shock that COVID-19 gave us unlike other viruses such as Ebola, the change was subtle. In other words, the world keeps going by coping with such challenges. Also, many reported that their health condition is in good shape. figure \@ref(fig:fig18)

@@
